---
title: "Course DEI Report"
author: "Ben"
date: "1/29/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This report first addresses single course (aggregated over many terms) grade penalties by:

1. Gender (1 = Female, 0 = male)

2. First Gen (1 = First gen)

3. URM (1 = URM)

Grades vs. GPAOs are given for each pair in 3 plots. These are followed by the results of a linear regression: `grade ~ GPAO + ACT_MATH + ACT_ENGL + SCHOOL + HS_GPA + ACAD_LVL + f(GENDER, URM, First Gen)` where `f` is the combination of interaction terms. In the table that follows the plots, we show
only the coefficients and the interaction terms.

## Results

```{r cars,echo=FALSE,message=FALSE,results="asis"}

source('~/Box Sync/SEISMIC/SEISMIC/course_performance_setup.R')
source('~/Box Sync/SEISMIC/SEISMIC/compare_performance.R')
data  <- course_performance_setup()
crse  <- data %>% distinct(scCNAME) 
ncrse <- dim(crse)[1]

for (i in 1:ncrse)
{
  print(crse$scCNAME[i])
  jj <- compare_performance(data %>% filter(data$scCNAME == crse$scCNAME[i]))
}

```
